Learning action models with minimal observability

### 2018-08-02 doc/aij18/aij18.tex
Added abstract

\begin{abstract}
  \textcolor[rgb]{1.00,0.00,0.00}{This paper presents a novel approach for learning \strips\ action models from observations of plan executions that compiles this learning task into classical planning. The compilation approach is flexible to various amount and kind of available input knowledge; learning examples can range from plans (with their corresponding initial state) to sequences of state observations or even just a set of initial and final states (where no intermediate action or state is known). The compilation accepts also partially specified action models and can be used to validate whether the observation of a plan execution follows a given \strips\ action model, even if this model is not fully specified. On the other hand, the compilation is extensible to assess how well a given \strips\ action model matches the observation of a plan execution. This extension allows us to evaluate the quality of the learned models with respect to the actual models but also, with respect to a {\em test set} of observations of plan executions. The performance of our compilation approach is evaluated learning action models, for a wide range of classical planning domains from the International Planning Competition (IPC), and following these two evaluation approaches.}
\end{abstract}

>>>>

\begin{abstract}
  This paper presents \FAMA, a novel approach for learning \strips\ action models from observations of plan executions that compiles the learning task into a classical planning task. Unlike all existing learning systems, \FAMA is able to learn when the actions of the plan executions are partially or totally unobservable and information on intermediate states is partially provided. This flexibility makes \FAMA an ideal learning approach in domains where only sensoring data are accessible. Additionally, we leverage the compilation scheme and extend it to come up with an evaluation method that allows us to assess the quality of a learned model syntactically, that is, with respect to the actual model; and, semantically, that is, with respect to a set of observations of plan executions. We also show that the extended compilation scheme can be used to lay the foundations of a framework for action model comparison. \FAMA is exhaustively evaluated over a wide range of IPC domains and its performance is compared to \ARMS, a state-of-the-art benchmark in action model learning.
\end{abstract}
